---
title: "Regression Discontinuity Design for Causality Discovery"
author: "haiyan yu"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Regression Discontinuity Design 

For treatment effect identification  of the honorary title in online healthcare communities, This function estimates the standard discontinuity regression:

$$Y=\alpha+\lambda D+\beta_1(X-c)+\beta_2(X-c)+\epsilon$$


#packages
```{r, include=FALSE}
#library("rddtools")

library("rdd")
library("rddtools")
 library(readxl)
```
# Data inputs
```{r}
treat_control <- read_excel("~/Downloads/treat_control.xlsx", 
     sheet = "ciewdf")
ctr.viewdf<-treat_control[complete.cases(treat_control),]
#award1<-ctr.viewdf
head(ctr.viewdf)
treat_control <- read_excel("~/Downloads/treat_control.xlsx", 
     sheet = "cpatdf")
ctr.patdf<-treat_control[complete.cases(treat_control),]
head(ctr.patdf)

treat_control <- read_excel("~/Downloads/treat_control.xlsx", 
     sheet = "tiewdf")
trt.viewdf<-treat_control[complete.cases(treat_control),]
#award1<-ctr.viewdf
head(trt.viewdf)

treat_control <- read_excel("~/Downloads/treat_control.xlsx", 
     sheet = "tpatdf")
trt.patdf<-treat_control[complete.cases(treat_control),]
head(trt.patdf)
nrow(trt.patdf)
```

#Data structure

```{r}
cut.off<-6
#trt.df<-trt.patdf
#ctr.df<-ctr.patdf


rdd_dat_indh <- rdd_data(#y=Patient,
                         y=ciewdf,
                         x=period,
                         data=ctr.viewdf,
                         cutpoint=cut.off)
#award<-sum_avg_award_paper
rdd_dat_indh2 <- rdd_data(#y=Patient,
                         y=tiewdf,
                         x=period,
                         data=trt.viewdf,
                         cutpoint=cut.off)

rdd_dat_indh3 <- rdd_data(#y=Patient,
                         y=cpatdf,
                         x=period,
                         data=ctr.patdf,
                         cutpoint=cut.off)
#award<-sum_avg_award_paper
rdd_dat_indh4 <- rdd_data(#y=Patient,
                         y=tpatdf,
                         x=period,
                         data=trt.patdf,
                         cutpoint=cut.off)


str(rdd_dat_indh)
str(rdd_dat_indh2)
#plot(y=award$patient1,  x=award$article, data=award)
#plot(y=award$patient1,  x=award$period, data=award)
summary(rdd_dat_indh)
head(rdd_dat_indh)
#df<-data.farme(award)
#award_rdd <- rdd_data(y=award$patient1, x=award$article, cutpoint=700)
#bandwidth<-1
#plot(rdd_dat_indh)
#plot(rdd_dat_indh2)
```
 
 
# Results comparison 

##monthly homepage views


```{r}
(reg_para <- rdd_reg_lm(rdd_dat_indh, order=1))
(reg_para2 <- rdd_reg_lm(rdd_dat_indh2, order=1))
 
s.d<-sd(ctr.viewdf$ciewdf)
rmin<- max(median(ctr.viewdf$ciewdf)-3*s.d,0)
rmax<-  median(ctr.viewdf$ciewdf)+1*s.d
#rmin<-min(ctr.viewdf$ciewdf)*0.9
#rmax<-max(trt.viewdf$tiewdf)*1.1
{
  plot(reg_para,xlab=c("Period"),ylab=c("Number of views"),ylim=range(rmin,rmax))
#use par and plot on the same graph but different axis. 
par(new=TRUE)
plot(reg_para2,xlab=c("Period"),ylab=c("Number of views"),ylim=range(rmin,rmax),   col = "red")
legend("bottomleft",legend=c("Control group","Awarded group"), pch=c(16,16),col = c("black","red"),horiz=F)#, title="Group"
abline(v = cut.off, col="blue", lwd=2, lty=2)
}
#(reg_para <- rdd_reg_lm(rdd_dat_indh, order=0))
#plot(reg_para,xlab=c("Period"),ylab=c("Number of patients"))

#(reg_para <- rdd_reg_lm(rdd_dat_indh, order=4))
#plot(reg_para,xlab=c("Period"),ylab=c("Number of patients"))
 
 
bw_ik <- rdd_bw_ik(rdd_dat_indh)
bw_ik2 <- rdd_bw_ik(rdd_dat_indh2)
(reg_nonpara <- rdd_reg_np(rdd_object=rdd_dat_indh, bw=bw_ik))
(reg_nonpara2 <- rdd_reg_np(rdd_object=rdd_dat_indh2, bw=bw_ik2))

rmin<- max(median(ctr.viewdf$ciewdf)-3*s.d,0)
rmax<-  median(ctr.viewdf$ciewdf)+1*s.d
{
  plot(reg_nonpara,xlab=c("Period"),ylab=c("Number of views"),ylim=range(rmin,rmax))
#use par and plot on the same graph but different axis. 
par(new=TRUE)
plot(reg_nonpara2,xlab=c("Period"),ylab=c("Number of views"),ylim=range(rmin,rmax),   col = "red")
legend("bottomleft",legend=c("Control group","Awarded group"), pch=c(16,16),col = c("black","red"),horiz=F)#, title="Group"
abline(v = cut.off, col="blue", lwd=2, lty=2)
}

```

### Sensitity tests.

```{r}
#plotSensi(reg_nonpara, from=1, to=70000, by=5000)
#all(is.na(reg_nonpara))
 
#plotPlacebo(reg_nonpara)

```

## Monthly online consultations

Data was demonstrated in the sets of  ctr.patdf v.s. trt.patdf. 

```{r}
(reg_para3 <- rdd_reg_lm(rdd_dat_indh3, order=1))
(reg_para4 <- rdd_reg_lm(rdd_dat_indh4, order=1))
 
s.d<-sd(ctr.patdf$cpatdf)
s.d2<-sd(trt.patdf$tpatdf)
rmin<- max(median(ctr.patdf$cpatdf)-1*s.d,0,median(trt.patdf$tpatdf)-1*s.d2)
rmax<-  max(median(ctr.patdf$cpatdf)+1*s.d, median(trt.patdf$tpatdf)+1*s.d2)
#rmin<-min(ctr.viewdf$ciewdf)*0.9
#rmax<-max(trt.viewdf$tiewdf)*1.1
{
  plot(reg_para3,xlab=c("Period"),ylab=c("Number of patients"),ylim=range(rmin,rmax),  col = "black")
par(new=TRUE)
plot(reg_para4,xlab=c("Period"),ylab=c("Number of patients"),ylim=range(rmin,rmax),   col = "red")
legend("bottomleft",legend=c("Control group","Awarded group"), pch=c(16,16),col = c("black","red"),horiz=F)#, title="Group"
abline(v = cut.off, col="blue", lwd=2, lty=2)
}
#(reg_para <- rdd_reg_lm(rdd_dat_indh, order=0))
#plot(reg_para,xlab=c("Period"),ylab=c("Number of patients"))

#(reg_para <- rdd_reg_lm(rdd_dat_indh, order=4))
#plot(reg_para,xlab=c("Period"),ylab=c("Number of patients"))
 
 
bw_ik <- rdd_bw_ik(rdd_dat_indh3)
bw_ik2 <- rdd_bw_ik(rdd_dat_indh4)
(reg_nonpara3 <- rdd_reg_np(rdd_object=rdd_dat_indh3, bw=bw_ik))
(reg_nonpara4 <- rdd_reg_np(rdd_object=rdd_dat_indh4, bw=bw_ik2))

#rmin<- max(median(ctr.viewdf$ciewdf)-3*s.d,0)
#rmax<-  median(ctr.viewdf$ciewdf)+1*s.d
{
plot(reg_nonpara3,xlab=c("Period"),ylab=c("Number of patients"),ylim=range(rmin,rmax))
par(new=TRUE)
plot(reg_nonpara4,xlab=c("Period"),ylab=c("Number of patients"),ylim=range(rmin,rmax),   col = "red")
legend("bottomleft",legend=c("Control group","Awarded group"), pch=c(16,16),col = c("black","red"),horiz=F)
abline(v = cut.off, col="blue", lwd=2, lty=2)
}

```

#Reference

[1] Imbens, Guido and Karthik Kalyanaraman. (2012) ’Optimal Bandwidth Choice for the regression discontinuity estimator,’ Review of Economic Studies (2012) 79, 933-959
[2]Guido Imbens webpage: http://scholar.harvard.edu/imbens/scholar_software/regression-discontinuity
[3] The oneline healthcare community: www.haodf.com
